Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-13 paper/latex/paper.tex
Added figures

Then, for both CNN with LSTM and ResNet, we computed the maximum accuracy over the epochs. Tab. \ref{epoch} compiles the number of samples per epoch and the total number of epochs used for each model and each value of $N$. Tab. \ref{class_res} shows the maximum accuracy computed using the function $f$ explicited in (\ref{eval}).

@@

\begin{table}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Instruments & \multicolumn{2}{c|}{$N=4$} & \multicolumn{2}{c|}{$N=5$}& \multicolumn{2}{c|}{$N=6$}& \multicolumn{2}{c|}{$N=7$}& \multicolumn{2}{c|}{$N=8$}& \multicolumn{2}{c|}{$N=9$}& \multicolumn{2}{c|}{$N=10$}\\
\cline{2-3} & C & R & C & R & C & R & C & R & C & R & C & R & C & R\\
\hline
All & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Hn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Ob & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Vn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Va & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Vc & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Fl & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Tbn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Bn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
TpC & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
ClBb & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
\hline
\end{tabular}

\begin{caption}
Best test accuracy obtained for each model and value of $N$ over the total number of epochs. The accuracy is computed using $f$ define in (\ref{eval}). The first row correspond to the overall accuracy of the model, regrouping all the instruments. C is CNN with LSTM, R is ResNet.
\label{class_res}
\end{caption}
\end{table}

@@

>>>>

Then, for both CNN with LSTM and ResNet, we computed the maximum accuracy over the epochs. Tab. \ref{epoch} compiles the number of samples per epoch and the total number of epochs used for each model and each value of $N$. Fig. \ref{cnn_vs_resnet} shows the best overall test accuracy achieved by both models across the number of instruments $N$ to detect simultaneously.\\

From this plot, we see that ResNet achieves better performances regardless of the number of instruments used in the combination, with

For more details on the accuracy Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum accuracy computed using the function $f$ explicited in (\ref{eval}).

@@

\begin{figure}
\includegraphics[scale=0.57]{figs/CNN_vs_ResNet.png}
\caption{Best overall accuracy and for CNN and ResNet depending on the number of instruments in the combinations used for training. \label{cnn_vs_resnet}}
\end{figure}

\iffalse
\begin{table*}
\center{
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Instruments & \multicolumn{2}{c|}{$N=4$} & \multicolumn{2}{c|}{$N=5$}& \multicolumn{2}{c|}{$N=6$}& \multicolumn{2}{c|}{$N=7$}& \multicolumn{2}{c|}{$N=8$}& \multicolumn{2}{c|}{$N=9$}& \multicolumn{2}{c|}{$N=10$}\\
\cline{2-3} & C & R & C & R & C & R & C & R & C & R & C & R & C & R\\
\hline
All & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Hn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Ob & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Vn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Va & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Vc & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Fl & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Tbn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
Bn & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
TpC & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
ClBb & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0\\
\hline
\end{tabular}

\begin{caption}
Best test accuracy obtained for each model and value of $N$ over the total number of epochs. The accuracy is computed using $f$ define in (\ref{eval}). The first row correspond to the overall accuracy of the model, regrouping all the instruments. C is CNN with LSTM, R is ResNet.
\label{class_res}
\end{caption}}
\end{table*}
\fi

@@

\begin{figure*}
\includegraphics[scale=0.6]{figs/Acc_vs_N_CNN.png}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM depending on the number of instruments in the combinations. \label{best_acc_cnn}}
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.6]{figs/Acc_vs_N_ResNet.png}
\caption{Best overall accuracy and for each instrument obtained by the ResNet depending on the number of instruments in the combinations. \label{best_acc_resnet}}
\end{figure*}
